analysis-pilot

### 2023-07-31 code/analysis-pilot.Rmd
having accurate looking timing date on transcripts!

timing <- raw_data |> group_by(game) |> mutate(cum_time=cumsum(time), cum_sec=cum_time/1000+3*trialNum)

@@

wrangle_transcript <- function(game_num){
readxl::read_xlsx(here("data/clean_transcripts", str_c(game_num,".xlsx"))) |> 
  select(start, end, text, speaker) |> 
  mutate(start=start/1000, end=end/1000) |> 
    nest(data=c(start, end, text, speaker))
}

@@

timed_transcripts <- transcripts |> mutate(start=start-offset_sec, end=end-offset_sec)
```

>>>>

@@

wrangle_transcript <- function(game_num){
read_csv(here("data/clean_transcripts", str_c(game_num,".csv"))) |> 
  select(start, end, text, speaker) |> 
  mutate(start=start/1000, end=end/1000) |> 
    nest(data=c(start, end, text, speaker))
}

@@

```{r, include=F, eval=F}
# a very derpy approach to aligning trial boundaries with transcripts

timing <- raw_data |> group_by(game) |> mutate(cum_time=cumsum(time), cum_sec=cum_time/1000+3*trialNum) |> select(trialNum, game, cum_sec) |> mutate(start=ifelse(trialNum==0, 0,lag(cum_sec)), end=cum_sec, trialNumStart=trialNum, trialNumEnd=trialNum, speaker=NA, text=NA) |> select(-cum_sec, -trialNum)

timed_transcripts <- transcripts |>
  mutate(start=start-offset_sec, end=end-offset_sec) |> 
  select(-offset_sec, -time, -gameId) |> 
  rename(game=gameConfig) |> 
  mutate(trialNumStart=NA, trialNumEnd=NA) |> 
  bind_rows(timing) |> 
  group_by(game) |> 
  arrange(start) |> 
  fill(trialNumStart) |> 
  arrange(end) |> 
  fill(trialNumEnd, .direction="up") |> 
  arrange(game) |> 
  filter(start>0)

# turns out this isn't good enough for timing, let's try stages instead!

stages <- read_csv(here("data/stages.csv")) |> select(index, gameId, startTimeAt) |> group_by(gameId)

gameStarts <- stages |> filter(index==0) |> rename(first=startTimeAt) |> select(-index)

stage_timing <- stages |> left_join(gameStarts) |> mutate(rel_time=startTimeAt-first) |> mutate(rel_time=lubridate::as.period(rel_time) |> lubridate::period_to_seconds()) |> filter(index%%2==0) |> mutate(trialNum=index/2) |> select(gameId, trialNum, start=rel_time, end=rel_time) |> left_join(games) |> mutate(trialNumStart=trialNum, trialNumEnd=lag(trialNum)) |> ungroup() |> select(game=gameConfig, trialNumStart, trialNumEnd, start, end) |> filter(!is.na(game)) |> filter(!is.na(start)) |> filter(!is.na(end))
```

```{r}
timed_transcripts <-  transcripts |>
  mutate(start=start-offset_sec, end=end-offset_sec) |> 
  select(-offset_sec, -time, -gameId) |> 
  mutate(trialNumStart=NA, trialNumEnd=NA) |> 
  rename(game=gameConfig) |> 
  bind_rows(stage_timing) |> 
  group_by(game) |> 
  arrange(start) |> 
  fill(trialNumStart) |> 
  arrange(end) |> 
  fill(trialNumEnd, .direction="up") |> 
  arrange(game) |> 
  filter(!is.na(text)) |> 
  write_csv(here("data/timed_transcript.csv"))
```
